Miniproject - Introduction to Schemes

### 2022-03-25 Schemes/submission.tex
Projective space is universally closed proven

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\A}{\mathbb{A}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\p}{\mathfrak{p}}
\newcommand{\q}{\mathfrak{q}}
\newcommand{\m}{\mathfrak{m}}
\renewcommand{\a}{\mathfrak{a}}
\renewcommand{\b}{\mathfrak{b}}
\renewcommand{\m}{\mathfrak{m}}
\newcommand{\Nil}{\mathfrak{N}}
\newcommand{\Set}{\mathrm{\textbf{Set}}}
\newcommand{\Aff}{\mathrm{\textbf{Aff}}}
\newcommand{\Sch}{\mathrm{\textbf{Sch}}}
\newcommand{\Ring}{\mathrm{\textbf{Ring}}}
\newcommand{\Ab}{\mathrm{\textbf{Ab}}}
\newcommand{\Top}{\mathrm{Top}}
\newcommand{\Spec}{\mathrm{Spec}}
\newcommand{\Proj}{\mathrm{Proj}}
\newcommand{\Frac}{\mathrm{Frac}}
\newcommand{\im}{\mathrm{im}}
\renewcommand{\O}{\mathcal{O}}
\DeclareMathOperator*{\colim}{colim}

@@

    Now consider the natural transformation
    \begin{equation*}
        \eta: \O_{\Spec R} \Rightarrow f_*\Bigl( \restr{\O_{\Proj(S)}}{D_f} \Bigr)
    \end{equation*}
    given on basic open sets by
    \begin{equation*}
        \eta_{D_{g/f^n}}: R_{g/f^n} \to (S_{fg})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
    \end{equation*}
    Clearly this is a ring isomorphism, so $\eta$ is a natural isomorphism.
    The claim follows.
\end{proof}
\begin{corollary}
    $(\Proj(S), \O_{\Proj(S)})$ is a scheme.
\end{corollary}
\begin{definition}
    For any ring $R$ and $n \in \N$, define the projective $n$-space as\footnote{Endow $R[x_0, ..., x_n]$ with the standard natural grading, i.e. $\deg(x_i) = 1$. Note that this makes $R[x_0, ..., x_n]_0 = R$, so all $r \in R$ are homogeneous of degree $0$.}
    \begin{equation*}
        \P_R^n := \Proj(R[x_0, ..., x_n])
    \end{equation*}
    which naturally becomes a scheme over $\Spec(R)$ via the morphism given by
    \begin{align*}
        &f: \Proj(R[x_0, ..., x_n]) \to \Spec(R), \quad \p \mapsto \p \cap R \\
        &f^\#_{D_f}: R_f \to \O_{\Proj(S)}(D_f) = (R[x_0, ..., x_n]_f)_0, \quad r \mapsto r
    \end{align*}
\end{definition}

@@

    So consider any nonempty basic open $D_f \subseteq \P_R^n$ and find that $D_f \cap D_{x_0} = D_{fx_0}$.
    By assumption, $\Nil(R)$ is a prime ideal and so $fx_0$ is not nilpotent (unless $f$ were nilpotent, but then $D_f = \emptyset$), i.e. the ring $R[x_0, ..., x_n]_{fx_0}$ is not the zero ring.
    Hence, it has a maximal ideal $\m$.
    Let $\p$ be the preimage of $\m$ under the localization map $R[x_0, ..., x_n] \to R[x_0, ..., x_n]_{fx_0}$, which is clearly prime with $fx_0 \notin \p$.
    By Lemma~\ref{prop:homogeneous_part_prime}, we now see that
    \begin{equation*}
        \p' := \langle f \in \p \ | \ \text{$f$ homogeneous} \rangle \leq R[x_0, ..., x_n]
    \end{equation*}
    is a homogeneous prime ideal, and since $fx_0 \notin \p \supseteq \p'$, we see that $S_+ \not\subseteq \p'$, i.e. $\p' \in \Proj(R[x_0, ..., x_n])$.
    Now it follows that $\p' \in D_{fx_0}$, so $D_{fx_0} \neq \emptyset$.
\end{proof}
\begin{prop}
    Assume $R$ is reduced.
    Then $\P_R^n$ is a reduced scheme.
\end{prop}
\begin{proof}
    By the lecture, it suffices to show that each $\O_{\P_R^n}(D_{x_i}) \cong \Spec(R[x_0, ..., x_n]_{x_i})_0$ is reduced.
    However this is trivial, as taking the polynomial ring $R[x_0, ..., x_n]$ preserves reducedness by Lemma~\ref{prop:nil_poly_ring}, and localizing (and of course taking the subring $S_0$) also do.
\end{proof}
\begin{corollary}
    Assume $R$ is integral.
    Then $\P_R^n$ is an integral scheme.
\end{corollary}
\begin{prop}
    $\P_R^n \to \Spec(R)$ is of finite type.
\end{prop}
\begin{proof}
    First note that $\P_R^n$ is covered by a finite number of affine opens $D_{x_i}$ where the canonical morphisms
    \begin{equation*}
        D_{x_i} \cong \Spec(R[x_0, ..., x_n]_{x_i})_0 \to \Spec(R)
    \end{equation*}
    are quasi-compact (they are induced by ring homomorphisms $R \to (R[x_0, ..., x_n]_{x_i})_0$), hence $\P_R^n$ is quasi-compact.

@@

\section{Projective space is proper}
We already know that $\P_R^n$ is separated and of finite type over $\Spec(R)$, hence it is left to show that it is universally closed.
\begin{lemma}
    Let $X, Y$ be topological spaces and $f: X \to Y$ a continuous map.
    Let further $Y = \bigcup_i V_i$ be a cover by open sets.
    If each of the maps
    \begin{equation*}
        \restr{f}{f^{-1}(V_i)}: f^{-1}(V_i) \to V_i
    \end{equation*}
    is closed (as a map into $V_i$), then $f$ is closed.
\end{lemma}
\begin{proof}
    Consider some closed $C \subseteq X$ and $x \in Y \setminus f(C)$.
    Since the $V_i$ cover $Y$, there is $i$ such that $x \in V_i$.
    As $\restr{f}{f^{-1}(V_i)}$ is closed, we see that
    \begin{equation*}
        f(C) \cap V_i = \restr{f}{f^{-1}(V_i)}(C)
    \end{equation*}
    is closed in $V_i$, hence there is an open neighborhood $U \subseteq V_i$ of $x$ with $U \cap f(C) = \emptyset$.
    Now note that $V_i \subseteq Y$ is open, and so $U$ is also an open neighborhood of $x$ in $Y$.
    This holds for all $x \in Y \setminus f(C)$, hence $f(C)$ is closed.
\end{proof}
\begin{corollary}
    A scheme $X$ over $\Spec(R)$ is universally closed, if for all ring homomorphisms $R \to S$ have the following:
    The map $X \times_{\Spec(R)} \Spec(S) \to \Spec(S)$ that makes the diagram
    \begin{center}
        \begin{tikzpicture}
            \node (SX) at (0, 0) {$\Spec(S) \times_{\Spec(R)} X$};
            \node (S) at (0, -1.5) {$\Spec(S)$};
            \node (X) at (4, 0) {$X$};
            \node (R) at (4, -1.5) {$\Spec(R)$};

            \draw [->] (SX) -- (S);
            \draw [->] (SX) -- (X);
            \draw [->] (S) -- (R);
            \draw [->] (X) -- (R);
        \end{tikzpicture}
    \end{center}
    is closed.
\end{corollary}
\begin{proof}
    Consider any scheme $Y$ over $\Spec(R)$.
    We have to show that the map $\pi: Y \times_{\Spec(R)} X \to Y$ that makes the diagram
    \begin{center}
        \begin{tikzpicture}
            \node (YX) at (0, 0) {$Y \times_{\Spec(R)} X$};
            \node (Y) at (0, -1.5) {$Y$};
            \node (X) at (4, 0) {$X$};
            \node (R) at (4, -1.5) {$\Spec(R)$};

@@

    In particular, any ring homomorphism $R \to S$ induces a canonical morphism $\P_S^n \to \P_R^n$ of schemes, since the induced ring homomorphism $R[x_0, ..., x_n] \to S[x_0, ..., x_n]$ satisfies the above additional condition.
\end{remark}
\begin{lemma}
    Let $S, T$ be $R$-algebras via $f: R \to S$ and $g: R \to T$.
    Let $\p \leq S, \q \leq T$ be prime ideals with $\b = f^{-1}(\p) = g^{-1}(\q)$.
    Then have the canonical map
    \begin{equation*}
        S \otimes_R T \to \Frac(S/\p) \otimes_R \Frac(T/\q) = \Frac{S/\p} \otimes_{R/\b} \Frac(T/\q)
    \end{equation*}
    Then the preimage $\a \leq S \otimes_R T$ of a prime ideal in $\Frac{S/\p} \otimes_{R/\b} \Frac(T/\q)$ is a prime ideal such that
    \begin{equation*}
        \iota_S^{-1}(\a) = \p \quad \text{and} \quad \iota_T^{-1}(\a) = \q
    \end{equation*}
    where $\iota_S: S \to S \otimes_R T$ and $\iota_T: T \to S \otimes_R T$ are the tensor maps.
\end{lemma}
\begin{lemma}
    Let $R \to S$ be a ring homomorphism.
    Then the base change of $\P_R^n$ is
    \begin{equation*}
        \P_R^n \times_{\Spec(R)} \Spec(S) = \P_S^n
    \end{equation*}
\end{lemma}
\begin{proof}
    Consider the canonical map $\alpha: R[x_0, ..., x_n] \to S[x_0, ..., x_n]$ induced by $R \to S$.
    Note that
    \begin{equation*}
        S \otimes_R (R[x_0, ..., x_n]_f)_0 \cong (S[x_0, ..., x_n]_{\alpha(f)})_0 \quad \text{via} \quad \iota_f: s \otimes \frac r {f^n} \mapsto \frac {s\alpha(r)} {\alpha(f)^n}
    \end{equation*}
    for all homogeneous $f \in R[x_0, ..., x_n]$.
    By Lemma~\ref{prop:Df_affine}, we see that $D_f$ for $f \in S[x_0, ..., x_n]$ homogeneous form an affine open cover of $\P_S^n$.
    Furthermore, we have a cover by affine opens $D_f \times_{\Spec(R)} \Spec(S)$ of $\P_R^n \times_{\Spec(R)} \Spec(S)$ for $f \in R[x_0, ..., x_n]$ homogeneous.
    Together, we see that it suffices to show that the isomorphisms (induced by $\iota_f$)
    \begin{equation*}
        \phi_f: D_{\alpha(f)} = \Spec((S[x_0, ..., x_n]_{\alpha(f)})_0) \to D_f \times_{\Spec(R)} \Spec(S)
    \end{equation*}
    glue to an isomorphism $\Proj(S[x_0, ..., x_n]) \to \P_R^n \times_{\Spec(R)} \Spec(S)$.
    By the gluing lemma, it suffices that the compatibility conditions are satisfied, i.e. that for all $f, g \in R[x_0, ..., x_n]$ homogeneous the diagram
    \begin{center}
        \begin{tikzpicture}
            \node (Sfg) at (0, 0) {$D_{\alpha(f)} \cap D_{\alpha(g)} = D_{\alpha(fg)}$};
            \node (Sf) at (3, 1) {$D_{\alpha(f)}$};
            \node (Sg) at (3, -1) {$D_{\alpha(g)}$};
            \node (f) at (7, 1) {$D_f \times_{\Spec(R)} \Spec(S)$};
            \node (g) at (7, -1) {$D_g \times_{\Spec(R)} \Spec(S)$};
            \node (all) at (10, 0) {$\P_R^n \times_{\Spec(R)} \Spec(S)$};

@@

    For a prime ideal $\p \in D_{\alpha(fg)}$ have that
    \begin{equation*}
        \phi_f(\p) = \iota_f^{-1}(\p \cap (S[x_0, ..., x_n]_f)_0) \in D_f \times_{\Spec(R)} \Spec(S)
    \end{equation*}
    and so $g \notin \phi_f(\p)$, i.e. $\phi_f(\p) \in D_{fg} \times_{\Spec(R)} \Spec(S)$.
    Hence, we have that both restrictions
    \begin{equation*}
        \restr{\phi_f}{D_{\alpha(fg)}}, \ \restr{\phi_g}{D_{\alpha(fg)}}: D_{\alpha(fg)} \to D_{fg} \times_{\Spec(R)} \Spec(S)
    \end{equation*}
    map into $D_{fg} \times_{\Spec(R)} \Spec(S)$.
    Now note that the diagram
    \begin{center}
        \begin{tikzpicture}
            \node (Rf) at (0, 0) {$S \otimes_R (R[x_0, ..., x_n]_f)_0$};
            \node (Rg) at (-3, -2) {$S \otimes_R (R[x_0, ..., x_n]_g)_0$};
            \node (Rfg) at (0, -4) {$S \otimes_R (R[x_0, ..., x_n]_{fg})_0$};

            \node (Sf) at (5, 0) {$(S[x_0, ..., x_n]_f)_0$};
            \node (Sg) at (8, -2) {$(S[x_0, ..., x_n]_g)_0$};
            \node (Sfg) at (5, -4) {$(S[x_0, ..., x_n]_{fg})_0$};

@@

            \draw [->] (Rf) -- (Rfg);
            \draw [->] (Rg) -- (Rfg);
            \draw [->] (Sf) -- (Sfg);
            \draw [->] (Sg) -- (Sfg);
        \end{tikzpicture}
    \end{center}
    commutes, and so the restrictions of $\phi_f$ resp. $\phi_g$ to $D_{\alpha(fg)}$ are both induced by the homomorphism $\iota_{fg}$, hence they are equal.
    The claim follows.
\end{proof}
\printbibliography
\end{document}

>>>>

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\A}{\mathbb{A}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\p}{\mathfrak{p}}
\newcommand{\q}{\mathfrak{q}}
\newcommand{\m}{\mathfrak{m}}
\renewcommand{\a}{\mathfrak{a}}
\renewcommand{\b}{\mathfrak{b}}
\renewcommand{\m}{\mathfrak{m}}
\newcommand{\Nil}{\mathfrak{N}}
\newcommand{\Set}{\mathrm{\textbf{Set}}}
\newcommand{\Aff}{\mathrm{\textbf{Aff}}}
\newcommand{\Sch}{\mathrm{\textbf{Sch}}}
\newcommand{\Ring}{\mathrm{\textbf{Ring}}}
\newcommand{\Ab}{\mathrm{\textbf{Ab}}}
\newcommand{\Top}{\mathrm{Top}}
\newcommand{\Spec}{\mathrm{Spec}}
\newcommand{\Proj}{\mathrm{Proj}}
\newcommand{\Frac}{\mathrm{Frac}}
\newcommand{\im}{\mathrm{im}}
\newcommand{\cont}{\mathrm{cont}}
\renewcommand{\O}{\mathcal{O}}
\DeclareMathOperator*{\colim}{colim}

@@

    Now consider the natural transformation
    \begin{equation*}
        \eta: \O_{\Spec R} \Rightarrow f_*\Bigl( \restr{\O_{\Proj(S)}}{D_f} \Bigr)
    \end{equation*}
    given on basic open sets by
    \begin{equation*}
        \eta_{D_{g/f^n}}: R_{g/f^n} \to (S_{fg})_0, \quad \frac {h/f^m} {(g/f^n)^l} \mapsto \frac {h f^{nl}} {g^l f^m}
    \end{equation*}
    Clearly this is a ring isomorphism, so $\eta$ is a natural isomorphism.
    The claim follows.
\end{proof}
\begin{corollary}
    $(\Proj(S), \O_{\Proj(S)})$ is a scheme.
\end{corollary}
\begin{definition}
    For any ring $R$ and $n \in \N$, define the projective $n$-space as\footnote{Endow $R[x_0, ..., x_n]$ with the standard natural grading, i.e. $\deg(x_i) = 1$. Note that this makes $R[x_0, ..., x_n]_0 = R$, so all $r \in R$ are homogeneous of degree $0$.}
    \begin{equation*}
        \P_R^n := \Proj(R[x_0, ..., x_n])
    \end{equation*}
    which naturally becomes a scheme over $\Spec(R)$ via the morphism given by
    \begin{align*}
        &f: \Proj(R[x_0, ..., x_n]) \to \Spec(R), \quad \p \mapsto \p \cap R \\
        &f^\#_{D_f}: R_f \to \O_{\Proj(R[x_0, ..., x_n])}(D_f) = (R[x_0, ..., x_n]_f)_0 = R_f, \quad r \mapsto r
    \end{align*}
\end{definition}

@@

    So consider any nonempty basic open $D_f \subseteq \P_R^n$ and find that $D_f \cap D_{x_0} = D_{fx_0}$.
    By assumption, $\Nil(R)$ is a prime ideal and so $fx_0$ is not nilpotent (unless $f$ were nilpotent, but then $D_f = \emptyset$), i.e. the ring $R[x_0, ..., x_n]_{fx_0}$ is not the zero ring.
    Hence, it has a maximal ideal $\m$.
    Let $\p$ be the preimage of $\m$ under the localization map $R[x_0, ..., x_n] \to R[x_0, ..., x_n]_{fx_0}$, which is clearly prime with $fx_0 \notin \p$.
    By Lemma~\ref{prop:homogeneous_part_prime}, we now see that
    \begin{equation*}
        \p' := \langle f \in \p \ | \ \text{$f$ homogeneous} \rangle \leq R[x_0, ..., x_n]
    \end{equation*}
    is a homogeneous prime ideal, and since $fx_0 \notin \p \supseteq \p'$, we see that $S_+ \not\subseteq \p'$, i.e. $\p' \in \Proj(R[x_0, ..., x_n])$.
    Now it follows that $\p' \in D_{fx_0}$, so $D_{fx_0} \neq \emptyset$.
\end{proof}
\begin{prop}
    Assume $R$ is reduced.
    Then $\P_R^n$ is a reduced scheme.
\end{prop}
\begin{proof}
    By the lecture, it suffices to show that each $\O_{\P_R^n}(D_{x_i}) \cong \Spec(R[x_0, ..., x_n]_{x_i})_0$ is reduced.
    However this is trivial, as taking the polynomial ring $R[x_0, ..., x_n]$ preserves reducedness by Lemma~\ref{prop:nil_poly_ring}, and localizing (and of course taking the subring $S_0$) also do.
\end{proof}
\begin{corollary}
    Assume $R$ is integral.
    Then $\P_R^n$ is an integral scheme.
\end{corollary}
\begin{prop}
    \label{prop:p_quasi_compact}
    $\P_R^n \to \Spec(R)$ is of finite type.
\end{prop}
\begin{proof}
    First note that $\P_R^n$ is covered by a finite number of affine opens $D_{x_i}$ where the canonical morphisms
    \begin{equation*}
        D_{x_i} \cong \Spec(R[x_0, ..., x_n]_{x_i})_0 \to \Spec(R)
    \end{equation*}
    are quasi-compact (they are induced by ring homomorphisms $R \to (R[x_0, ..., x_n]_{x_i})_0$), hence $\P_R^n$ is quasi-compact.

@@

\section{Projective space is proper}
We already know that $\P_R^n$ is separated and of finite type over $\Spec(R)$, hence it is left to show that it is universally closed.
\begin{lemma}
    Let $X, Y$ be topological spaces and $f: X \to Y$ a continuous map.
    Let further $Y = \bigcup_i V_i$ be a cover by open sets.
    If each of the maps
    \begin{equation*}
        \restr{f}{f^{-1}(V_i)}: f^{-1}(V_i) \to V_i
    \end{equation*}
    is closed (as a map into $V_i$), then $f$ is closed.
\end{lemma}
\begin{proof}
    Consider some closed $C \subseteq X$ and $x \in Y \setminus f(C)$.
    Since the $V_i$ cover $Y$, there is $i$ such that $x \in V_i$.
    As $\restr{f}{f^{-1}(V_i)}$ is closed, we see that
    \begin{equation*}
        f(C) \cap V_i = \restr{f}{f^{-1}(V_i)}(C)
    \end{equation*}
    is closed in $V_i$, hence there is an open neighborhood $U \subseteq V_i$ of $x$ with $U \cap f(C) = \emptyset$.
    Now note that $V_i \subseteq Y$ is open, and so $U$ is also an open neighborhood of $x$ in $Y$.
    This holds for all $x \in Y \setminus f(C)$, hence $f(C)$ is closed.
\end{proof}
\cite[66.9.5.]{stacks}
\begin{corollary}
    \label{prop:universally_closed_affines}
    A scheme $X$ over $\Spec(R)$ is universally closed, if for all ring homomorphisms $R \to S$ have the following:
    The base change map $X \times_{\Spec(R)} \Spec(S) \to \Spec(S)$, i.e. the map that makes the diagram
    \begin{center}
        \begin{tikzpicture}
            \node (SX) at (0, 0) {$\Spec(S) \times_{\Spec(R)} X$};
            \node (S) at (0, -1.5) {$\Spec(S)$};
            \node (X) at (4, 0) {$X$};
            \node (R) at (4, -1.5) {$\Spec(R)$};

            \draw [->] (SX) -- (S);
            \draw [->] (SX) -- (X);
            \draw [->] (S) -- (R);
            \draw [->] (X) -- (R);
        \end{tikzpicture}
    \end{center}
    commute, is closed.
\end{corollary}
\begin{proof}
    Consider any scheme $Y$ over $\Spec(R)$.
    We have to show that the map $\pi: Y \times_{\Spec(R)} X \to Y$ that makes the diagram
    \begin{center}
        \begin{tikzpicture}
            \node (YX) at (0, 0) {$Y \times_{\Spec(R)} X$};
            \node (Y) at (0, -1.5) {$Y$};
            \node (X) at (4, 0) {$X$};
            \node (R) at (4, -1.5) {$\Spec(R)$};

@@

    In particular, any ring homomorphism $R \to S$ induces a canonical morphism $\P_S^n \to \P_R^n$ of schemes, since the induced ring homomorphism $R[x_0, ..., x_n] \to S[x_0, ..., x_n]$ satisfies the above additional condition.
\end{remark}
\begin{lemma}
    \label{prop:projective_space_base_change}
    Let $R \to S$ be a ring homomorphism.
    Then the base change of $\P_R^n$ is
    \begin{equation*}
        \P_R^n \times_{\Spec(R)} \Spec(S) \cong \P_S^n
    \end{equation*}
    as schemes over $\Spec(S)$.
\end{lemma}
\begin{proof}
    Consider the canonical map $\alpha: R[x_0, ..., x_n] \to S[x_0, ..., x_n]$ induced by $R \to S$.
    Note that
    \begin{equation*}
        S \otimes_R (R[x_0, ..., x_n]_f)_0 \cong (S[x_0, ..., x_n]_{\alpha(f)})_0 \quad \text{via} \quad \iota_f: s \otimes \frac r {f^n} \mapsto \frac {s\alpha(r)} {\alpha(f)^n}
    \end{equation*}
    for all homogeneous $f \in R[x_0, ..., x_n]$.
    By Lemma~\ref{prop:Df_affine}, we see that $D_f$ for $f \in S[x_0, ..., x_n]$ homogeneous form an affine open cover of $\P_S^n$.
    Furthermore, we have a cover by affine opens $D_f \times_{\Spec(R)} \Spec(S)$ of $\P_R^n \times_{\Spec(R)} \Spec(S)$ for $f \in R[x_0, ..., x_n]$ homogeneous.
    Together, we see that it suffices to show that the isomorphisms (induced by $\iota_f$)
    \begin{equation*}
        \phi_f: D_{\alpha(f)} = \Spec((S[x_0, ..., x_n]_{\alpha(f)})_0) \to D_f \times_{\Spec(R)} \Spec(S)
    \end{equation*}
    glue to an isomorphism $\Proj(S[x_0, ..., x_n]) \to \P_R^n \times_{\Spec(R)} \Spec(S)$.
    By the gluing lemma, it suffices that the compatibility conditions are satisfied, i.e. that for all $f, g \in R[x_0, ..., x_n]$ homogeneous the diagram
    \begin{center}
        \begin{tikzpicture}
            \node (Sfg) at (0, 0) {$D_{\alpha(f)} \cap D_{\alpha(g)} = D_{\alpha(fg)}$};
            \node (Sf) at (3, 1) {$D_{\alpha(f)}$};
            \node (Sg) at (3, -1) {$D_{\alpha(g)}$};
            \node (f) at (7, 1) {$D_f \times_{\Spec(R)} \Spec(S)$};
            \node (g) at (7, -1) {$D_g \times_{\Spec(R)} \Spec(S)$};
            \node (all) at (10, 0) {$\P_R^n \times_{\Spec(R)} \Spec(S)$};

@@

    For a prime ideal $\p \in D_{\alpha(fg)}$ have that
    \begin{equation*}
        \phi_f(\p) = \iota_f^{-1}(\p \cap (S[x_0, ..., x_n]_f)_0) \in D_f \times_{\Spec(R)} \Spec(S)
    \end{equation*}
    and so $g \notin \phi_f(\p)$, i.e. $\phi_f(\p) \in D_{fg} \times_{\Spec(R)} \Spec(S)$.
    Hence, we have that both restrictions
    \begin{equation*}
        \restr{\phi_f}{D_{\alpha(fg)}}, \ \restr{\phi_g}{D_{\alpha(fg)}}: D_{\alpha(fg)} \to D_{fg} \times_{\Spec(R)} \Spec(S)
    \end{equation*}
    map into $D_{fg} \times_{\Spec(R)} \Spec(S)$.
    Now note that the diagram
    \begin{center}
        \begin{tikzpicture}
            \node (Rf) at (-3, 0) {$S \otimes_R (R[x_0, ..., x_n]_f)_0$};
            \node (Rg) at (0, -2) {$S \otimes_R (R[x_0, ..., x_n]_g)_0$};
            \node (Rfg) at (-3, -4) {$S \otimes_R (R[x_0, ..., x_n]_{fg})_0$};

            \node (Sf) at (8, 0) {$(S[x_0, ..., x_n]_f)_0$};
            \node (Sg) at (5, -2) {$(S[x_0, ..., x_n]_g)_0$};
            \node (Sfg) at (8, -4) {$(S[x_0, ..., x_n]_{fg})_0$};

@@

            \draw [->] (Rf) -- (Rfg);
            \draw [->] (Rg) -- (Rfg);
            \draw [->] (Sf) -- (Sfg);
            \draw [->] (Sg) -- (Sfg);
        \end{tikzpicture}
    \end{center}
    commutes, and so the restrictions of $\phi_f$ resp. $\phi_g$ to $D_{\alpha(fg)}$ are both induced by the homomorphism $\iota_{fg}$, hence they are equal.
    The claim follows.
\end{proof}
The next lemma is directly from \cite[II.4.5]{hartshorne}.
\begin{lemma}
    \label{prop:im_closed_iff_stable_specialization}
    Let $f: X \to Y$ be a quasi-compact morphism.
    Then $f(|X|)$ is closed if and only if it is stable under specialization.
\end{lemma}
\begin{lemma}
    \label{prop:adding_coeff_ideal_does_not_introduce_irrelevant_ideal}
    Let $\p \leq R[x_0, ..., x_n]$ be a homogeneous prime ideal with $R[x_0, ..., x_n]_+ \not\subseteq \p$.
    Further let $\q \leq R$ be a prime ideal such that $\p \cap R \subseteq \q$.
    Then there some $i$ such that no $\alpha x_i^m$ is in $\b := \p + \q R[x_0, ..., x_n]$, for any $\alpha \in R \setminus \b$ and any $m \in \N$.
\end{lemma}
\begin{proof}
    Assume there is $m \in \N$ such that $\alpha_i x_i^m \in \b$ for all $i$ and some $\alpha_i \in \b \setminus R$.
    Since $\b \cap R = \q$ is prime, have that $\alpha := \prod_i \alpha_i \notin \b$.
    Further we have that $\alpha x_i^m \in \b$ for all $i$.

    Consider now the vector $(w_i)_{i < N}$ containing all monomials of degree $(n + 1)m$.
    By assumption, all $\alpha w_i \in \b$.
    Since $\p$ is homogeneous, observe that now there are $r_{ij} \in \q$ such that
    \begin{equation*}
        \alpha w_i - \sum_{j < N} r_{ij} w_j \in \p
    \end{equation*}
    Working modulo $\p$, we see that $A w = \alpha w$ where $A \in (\b/\p)^{N \times N}$.

    Now observe that $\alpha \notin \b/\p$ since $\alpha \notin \b$.
    Hence there exists a prime ideal in $R/\p$ containing $\b/\p$ and not containing $\alpha$.
    Localizing at that prime ideal gives a local ring $S$ with maximal ideal $\mathfrak{l}$.
    Now assume that $w \in S^n$ and $A/\alpha \in \mathfrak{l}^{n \times n}$.
    Note that we still have $(A/\alpha) w = w$.

    wlog $S$ is noetherian, otherwise continue with the ring
    \begin{equation*}
        \tilde{S} := \begin{cases}
            \Z[A/\alpha, x] & \text{if $\mathrm{char}(S) = 0$} \\
            (\Z/\mathrm{char}(R)\Z)[A/\alpha, x] & \text{if $\mathrm{char}(S) \neq 0$}
        \end{cases}
    \end{equation*}
    generated by the coefficients of $A/\alpha$ and $w$ (this is noetherian, as it is a quotient of a polynomial ring in finitely many variables).

    Now equip $S_{\mathfrak{l}}$ with the $\mathfrak{l}$-adic topology.
    Note that $S$ is noetherian and local, thus the Krull intersection theorem shows that the $\mathfrak{l}$-adic topology is Hausdorff and we find
    \begin{equation*}
        w = \lim_{i \to \infty} w = \lim_{i \to \infty} \frac {A^i} {\alpha^i} w = \Bigl( \lim_{i \to \infty} \frac {A^i} {\alpha^i} \Bigr) w = 0 w = 0
    \end{equation*}
    since $(A/\alpha)^i$ has coefficients in $\mathfrak{l}^i$, thus converges to $0$ as $i \to \infty$.

    Thus $w \equiv 0 \mod \p$ and so $x_i^N \equiv 0 \mod \p$, i.e. $x_i^N \in \p$ for all $i$.
    However, since $\p$ is prime, this implies $R[x_0, ..., x_n]_+ = \langle x_0, ..., x_n \rangle \subseteq \p$, contradicting the assumption. 
\end{proof}
\begin{prop}
    \label{prop:projective_structure_morphism_closed}
    The morphism $\P_R^n \to \Spec(R)$ is closed.
\end{prop}
\begin{proof}
    Denote $\P_R^n \to \Spec(R)$ by $\phi$.
    Consider a closed set $\V(\a) = \P_R^n \setminus D_\a$ given by a homogeneous ideal $\a \leq R[x_0, ..., x_n]$.
    By Lemma~\ref{prop:im_closed_iff_stable_specialization}, it suffices to show that $\phi(\V(\a))$ is closed under specialization (note that $\P_R^n \to \Spec(R)$ is quasi-compact, e.g. by Proposition~\ref{prop:p_quasi_compact}).

    Consider $\q \in \phi(\V(\a)) \subseteq \Spec(R)$ and a prime ideal $\q'$ that specializes $\q$, i.e. $\q' \supseteq \q$.
    Then there is a $\p \in \V(\a)$ with $\p \cap R = \q$, in particular $\a \subseteq \p$.
    We want to show that $\q' \in \phi(\V(\a))$.

    Note that by Lemma~\ref{prop:adding_coeff_ideal_does_not_introduce_irrelevant_ideal}, there is $i$ such that the multiplicative set
    \begin{equation*}
        T := \{ \alpha x_i^m \ | \ \alpha \in R \setminus \q', \ m \in \N \}
    \end{equation*}
    has empty intersection with the ideal $\b := \p + \q' R[x_0, ..., x_n]$.

    Hence, the ring $T^{-1}(R[x_0, ..., x_n]/\b)$ is nonzero, thus has a prime.
    Taking its preimage under
    \begin{equation*}
        R[x_0, ..., x_n] \to R[x_0, ..., x_n]/\b \to T^{-1}(R[x_0, ..., x_n]/\b)
    \end{equation*}
    yields a prime ideal $\p'$ such that $x_i \notin \p'$ and $\b \subseteq \p'$.
    Clearly have that $\q' \subseteq \p'$ and since $\p' \cap T = \emptyset$, find that $\p' \cap R = \q'$.
    By Lemma~\ref{prop:homogeneous_part_prime}, assume wlog that $\p'$ is homogeneous.
    Now have a homogeneous prime ideal $\p'$ with $\a \subseteq \p \subseteq \p'$, i.e. $\p' \in \V(\a)$ and $\phi(\p') = \p' \cap R = \q'$.
    Thus $\q \in \phi(\V(\a))$ and the claim follows.
\end{proof}
\begin{corollary}
    The morphism $\P_R^n \to \Spec(R)$ is universally closed.
\end{corollary}
\begin{proof}
    Use Lemma~\ref{prop:universally_closed_affines}, so consider an affine base change $f_{\Spec(S)}: \P_R^n \times_{\Spec(R)} \Spec(S) \to \Spec(S)$.
    By Lemma~\ref{prop:projective_space_base_change}, have that $\P_R^n \times_{\Spec(R)} \Spec(S) \cong \P_S^n$ as schemes over $S$, hence $f_{\Spec(S)}$ is isomorphic to $\P_S^n \to \Spec(S)$.
    This morphism is closed by Proposition~\ref{prop:projective_structure_morphism_closed} and the claim follows.
\end{proof}
\begin{corollary}
    Projective space $\P_R^n$ over $\Spec(R)$ is proper.
\end{corollary}
\begin{corollary}
    Let $k$ be an algebraically closed field.
    Then projective space $\P_k^n$ over $\Spec(k)$ is a complete variety.
\end{corollary}

\section{Valuative criterion of properness}
\begin{prop}
    Let $X$ be noetherian and $f: X \to Y$ a morphism of finite type.
    The following are equivalent
    \begin{itemize}
        \item $f$ is proper
        \item For every valuation ring $R$ with field of fractions $K = \Frac(R)$ and all morphisms $\Spec(R) \to Y$, $\Spec(K) \to X$ that make the diagram
        \begin{center}
            \begin{tikzpicture}
                \node (K) at (0, 0) {$\Spec(K)$};
                \node (R) at (0, -2) {$\Spec(R)$};
                \node (X) at (3, 0) {$X$};
                \node (Y) at (3, -2) {$Y$};

                \draw [->] (K) -- (R);
                \draw [->] (K) -- (X);
                \draw [->] (R) -- (Y);
                \draw [->] (X) -- (Y) node [midway, right] {$f$};
            \end{tikzpicture}
        \end{center}
        commute, there exists a unique compatible morphism $\Spec(R) \to X$.
    \end{itemize}
\end{prop}
\printbibliography
\end{document}
